Simple and Transparent Macroeconomic Prediction Intervals

### 2023-09-26 presentation/presentation.tex
update presentation files

\begin{columns}
\begin{column}{0.6\textwidth}
    \begin{figure}
        \centering
        \includegraphics[width=\textwidth]{figures/horizon_uncc.pdf}
        %\caption{Coverage at the 50 and 80 percent level}
        \label{fig:enter-label}
    \end{figure}
\end{column}
\begin{column}{0.4\textwidth}
\centering
\textbf{Average length of intervals}
\begin{table}
\begin{tabular}{ l c c }
&   50\%  & 80\%\\[0.3em]
\multicolumn{3}{c}{\textbf{GDP Growth}}\\
Fall,  SY & 0.5 & 0.9\\ 
Spring, SY &0.8 &2.1 \\ 
Fall, NY & 2.2 & 3.9\\ 
Spring, NY &2.4 &4.9 \\[0.3em] 
\multicolumn{3}{c}{\textbf{Inflation}}\\
%&   50\%  & 80\%\\[0.3em]
Fall,  SY & 0.3 & 0.6\\ 
Spring, SY &0.5 &1.3 \\ 
Fall, NY & 1.2 & 2.2\\ 
Spring, NY &1.9 &2.4 \\ 
\end{tabular}
\end{table}
\vspace{1.25cm}
%\begin{table}
%\begin{tabular}{ l c c }
%\multicolumn{3}{c}{\textbf{Inflation}}\\
%%&   50\%  & 80\%\\[0.3em]
%Fall,  SY & 0.3 & 0.6\\ 
%Spring, SY &0.5 &1.3 \\ 
%Fall, NY & 1.2 & 2.2\\ 
%Spring, NY &1.9 &2.4 \\ 
%\end{tabular}
%\end{table}
\end{column}
\end{columns}

@@

\begin{frame}{Robustness Checks}
\textit{each will be linked to a short slide in Appendix giving the alternative results}
\begin{itemize}
    \item error extraction method: absolute vs. directional errors
    \item window method
    \item potential dependency of results on discretization \\
    \textit{what I mean by this: does the fact that we are extracting quantiles from the samples influence the results? Show results for sample-based CRPS}
\end{itemize}
\end{frame}

>>>>

\begin{columns}
\begin{column}{0.6\textwidth}
    \begin{figure}
        \centering
        \includegraphics[width=\textwidth]{figures/horizon_uncc.pdf}
        %\caption{Coverage at the 50 and 80 percent level}
        \label{fig:enter-label}
    \end{figure}
\end{column}
\begin{column}{0.4\textwidth}
\centering
\textbf{Average length of intervals}
\begin{table}
\begin{tabular}{ l c c }
&   50\%  & 80\%\\[0.3em]
\multicolumn{3}{c}{\textbf{GDP Growth}}\\
Fall,  SY & 0.5 & 1.1\\ 
Spring, SY &1.2 &2.1 \\ 
Fall, NY & 1.9 & 3.5\\ 
Spring, NY &2.2 &4.0 \\[0.3em] 
\multicolumn{3}{c}{\textbf{Inflation}}\\
%&   50\%  & 80\%\\[0.3em]
Fall,  SY & 0.3 & 0.5\\ 
Spring, SY &0.6 &1.1 \\ 
Fall, NY & 1.1 & 1.8\\ 
Spring, NY &1.3 &2.1 \\ 
\end{tabular}
\end{table}
\vspace{1.25cm}
%\begin{table}
%\begin{tabular}{ l c c }
%\multicolumn{3}{c}{\textbf{Inflation}}\\
%%&   50\%  & 80\%\\[0.3em]
%Fall,  SY & 0.3 & 0.6\\ 
%Spring, SY &0.5 &1.3 \\ 
%Fall, NY & 1.2 & 2.2\\ 
%Spring, NY &1.9 &2.4 \\ 
%\end{tabular}
%\end{table}
\end{column}
\end{columns}

%\textit{relate back to article shown in the beginning, which also mentions IMF forecast of 0.1 percent $\rightarrow$ almost 50\% of any predictive intervals at this time would actually be below zero}
\end{frame}
\addtocounter{framenumber}{-1}
\begin{frame}{Will Germany avoid recession?}
%Width of Prediction Intervals, by Horizon
%\textit{include graphic or table showing increasing uncertainty with rising horizons}\\ 
\begin{figure}
        \centering
        \includegraphics[width=0.6\textwidth]{figures/horizon_uncc_germany2023.pdf}
        %\caption{Coverage at the 50 and 80 percent level}
        \label{fig:enter-label}
    \end{figure}

@@

\begin{frame}{Robustness Checks}
\textit{each will be linked to a short slide in Appendix giving the alternative results}
\begin{itemize}
    \item error extraction method: absolute vs. directional errors
    \item window method
    \item potential dependency of results on quantile extraction \\
    \textit{what I mean by this: does the fact that we are extracting quantiles from the samples influence the results? Show results for sample-based CRPS}
\end{itemize}
\end{frame}
